Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-08-17 paper/paper.tex
Fixing figures

The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.  All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps}, which has coverage from 1972 through 2013 and are on a 1--hour time grid. $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly median over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used. GOES 6 had the longest span of available data and the primary results presented are for GOES 6 while measurements from other satellites were used for consistency checks.

>>>>

The parameters $\rho_{eq}$ and $F_{10.7}$ are from the dataset of \cite{Takahashi2010}; data are available from 1980 through 1991 from GOES 2, 3, 5, 6 and 7.  All other parameters used are from \cite{Kondrashov2014ReconstructionOfGaps}, which has coverage from 1972 through 2013 and are on a 1--hour time grid. $\rho_{eq}$ is the inferred equatorial mass density based on the 3rd harmonic torodial frequency of magnetic field measurements as described in \cite{Takahashi2010}.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly median over the same interval for which the solar wind parameters were averaged, the median of all $\rho_{eq}$ values in a given hour window was used. GOES 6 had the longest span of available (May 1983 to August 1991) data and the primary results presented are for GOES 6 while measurements from other satellites were used for consistency checks.
